Convergence rate of MAP estimates \\ for the exponential family

### 2021-05-31 main.tex
Add shadow boxes and clean figure links

% frames with colored background
\definecolor{light-gray}{gray}{0.85}
\definecolor{myblue}{RGB}{199, 235, 255}
\usepackage[framemethod=TikZ]{mdframed} 
\usetikzlibrary{shadows}

\newmdenv[% box with grey background
    backgroundcolor=gray!15,
    linewidth=0pt,
    roundcorner=5pt,
    shadow=true,
	shadowsize=4pt
]{example}
\newmdenv[
	backgroundcolor=myblue,
	roundcorner=5pt, 
	linewidth=0pt, 
	shadow=true,
	shadowsize=4pt
]{important}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{figs/numerical_schema_n=3.pdf}
	\caption{A numerical illustration of the different characters featured in the bias-variance decomposition, for a 1D Gaussian $\cN(\mu, \sigma^2)$.}
	\label{fig:bias-variance-numerical}
\end{figure}

>>>>

% frames with colored background
\definecolor{light-gray}{gray}{0.85}
\definecolor{myblue}{RGB}{199, 235, 255}
\usepackage[framemethod=TikZ]{mdframed} 
\usetikzlibrary{shadows}
% Using the pgf-blur package instead 
% https://ctan.math.illinois.edu/graphics/pgf/contrib/pgf-blur/pgf-blur.pdf
\usetikzlibrary{shadows.blur}

\mdfdefinestyle{blurry-shadow}{
	linewidth=0pt,
    roundcorner=0pt,
	shadow=true,
 	apptotikzsetting={\tikzset{mdfshadow/.style={blur shadow={%
 		shadow xshift=1pt,
 		shadow yshift=-1pt,
 		shadow scale=1.00,
 		shadow opacity = 50,
 		%shadow blur extra rounding,
 		shadow blur steps = 10,
 		shadow blur radius = 5pt,
 		every shadow
 	}}}},
	linewidth=0pt,
 }

\newmdenv[% box with grey background
	style=blurry-shadow,
    backgroundcolor=gray!15,
]{example}
\newmdenv[
	style=blurry-shadow,
	backgroundcolor=myblue,
]{important}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=\textwidth]{figs/thales/numerical_schema_n=1.pdf}
	\includegraphics[width=\textwidth]{figs/thales/numerical_schema_n=2.pdf}
	\includegraphics[width=\textwidth]{figs/thales/numerical_schema_n=3.pdf}
	\includegraphics[width=\textwidth]{figs/thales/numerical_schema_n=10.pdf}
	\caption{A numerical illustration of the different characters featured in the bias-variance decomposition, for a 1D Gaussian $\cN(\mu, \sigma^2)$.}
	\label{fig:bias-variance-numerical}
\end{figure}
